\chapter{Future Work}
Significant improvements to the genetic algorithm as well as to the Traffic Manger are possible. Two main paths seem to provide valuable enhancements.

\section{Additional Actions}
Although the provided actions by the Action Interface (see section \ref{sect:implementation:action_interface}) already produce a vast search space, additional actions might improve variation in the results and provide even more complex critical scenarios. Examples for new actions are applying a lane offset, ignoring red traffic lights or simulating a blown tire.

Implementing these actions will in some cases require only minimal effort and will allow a genetic algorithm to use even more complex action sequences for its search.

\section{Oracles}
Utilizing oracle functions in order to select interesting scenarios during the runtime of a genetic algorithm was already done by \cite{almanee_scenorita_2021}. Multiple oracle functions will test for different thresholds. For example, one oracle function might check, if the ego vehicle has exceeded the speed limit, a different function checks for crashes where the ego vehicle is at fault. Other ideas include having an oracle which evaluates if the comfort level of the passenger is under a certain threshold.\todo{add Responsibility-Sensitive Safety (RSS)}

These functions will test each individual in the population. In case one or multiple functions return true, the individual scenario will be saved and automatically categorized according to the types of thresholds. The genetic algorithm however remains unaffected.

Oracles have the potential to extract multiple different scenarios from only one genetic algorithm run. The automatic categorization drastically improves the usefulness of this testing approach. Otherwise each search result needs to be evaluated manually for finding errors in the autonomous driving system.


